### 2021-10-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@ae9a1cdc5f3d535fa0e5ab43ba94a49ee154d4c4 🚀

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Phenological uncoupling (\textbf{Olesen2011MisFor?}).
\end{enumerate}

@@

In this paper we\ldots. combine data from a variety of sources: field
data from several sites, crowd-sourced data (GBIF), and remotely-sensed
data. to produce a \emph{spatially and temporally explict} metaweb of
bumblebee-flower interactions across Colorado. We then estimate the
change in spatial and temporal overlap over time using the CMIP6 climate
consensus forecast (\textbf{Karger2017CliHig?}).

@@

The remote-sensing data consists of high-resolution LiDAR elevation data
at 1 meter spatial resolution
{[}(\textbf{NationalEcologicalObservatoryNetworkNEON2021EleLid?});{]},
and daily 1km resolution precipitation and temperature from CHELSA
(\textbf{Karger2021GloDai?}).

@@

\hypertarget{a-predictive-model-to-make-spatially-explicit-network-prediction}{%
\subsection{A predictive model to make spatially explicit network
prediction}\label{a-predictive-model-to-make-spatially-explicit-network-prediction}}

The goal is two have two predictive models: interaction-predictor model
and a distribution-predictor model (a la Strydom \& Catchen et al.~2021,
figure 2).

The interaction-predictor model, \(f_i(s_i,s_j, \theta_i)\) predicts
interaction based on species-level features \((s_i, s_j)\), and is
trained on the field-data.

These features could include Phylogeny (to be determined: how available
are genomes or trees for these species) Environment/Climate Traits (to
be determined: what trait data is available, how annoying is it to
clean) Time (only for the phenology model, see 3.2 and 3.3)

The distribution-predictor model, \(f_s(s_i, \vec{x}, t)\) is trained on
GBIF data to predict the occurrence of species with features si at a
location in space x, and time t. Many options here. Here the species
level features could be Climatic variables derived from remote sensing
products. Co-occurence to make a JSDM Potentially weighted by phenology
information from field data. Time (only for the phenology model, see 3.2
and 3.3)

\hypertarget{combining-distribution-predictor-and-interaction-predictor-models}{%
\subsection{Combining distribution-predictor and interaction-predictor
models}\label{combining-distribution-predictor-and-interaction-predictor-models}}

Can split this into two based on how the distribution-predictor works.
If \(f_s\) predicts co-occurrence, then draw the species pool first and
predict interactions between the species in that pool. If \(f_s\) is a
single-species SDM, get the occurrence probability for each species p\_s
and compute the probability of observing interaction as function of the
product of occ. prob.

@@

\hypertarget{references}{%
\section{References}\label{references}}

>>>>

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Phenological uncoupling (Olesen \emph{et al.} 2011).
\end{enumerate}

@@

In this paper we\ldots. combine data from a variety of sources: field
data from several sites, crowd-sourced data (GBIF), and remotely-sensed
data. to produce a \emph{spatially and temporally explict} metaweb of
bumblebee-flower interactions across Colorado. We then estimate the
change in spatial and temporal overlap over time using the CMIP6 climate
consensus forecast (Karger \emph{et al.} 2017).

@@

The remote-sensing data consists of high-resolution LiDAR elevation data
at 1 meter spatial resolution {[}(NEON) (2021);{]}, and daily 1km
resolution precipitation and temperature from CHELSA (Karger \emph{et
al.} 2021).

@@

\hypertarget{model-fitting-and-validation}{%
\subsection{Model fitting and
validation}\label{model-fitting-and-validation}}

Models are implemented and fitted in Julia v1.6, using Turing.jl
{[}cite{]}

\hypertarget{training-test-validation-split-scheme}{%
\subsubsection{Training-test-validation split
scheme}\label{training-test-validation-split-scheme}}

How do this? Do we remove sites entirely? Years entirely? Perhaps pikes
peak would be best as a validation set as its only one year anyway and
is a larger elevation gradient.

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Karger2017CliHig}{}%
Karger, D.N., Conrad, O., Böhner, J., Kawohl, T., Kreft, H., Soria-Auza,
R.W., \emph{et al.} (2017). Climatologies at high resolution for the
earth's land surface areas. \emph{Scientific Data}, 4, 170122.

\leavevmode\hypertarget{ref-Karger2021GloDai}{}%
Karger, D.N., Wilson, A.M., Mahony, C., Zimmermann, N.E. \& Jetz, W.
(2021). Global daily 1km land surface precipitation based on cloud
cover-informed downscaling. \emph{arXiv:2012.10108 {[}physics{]}}.

\leavevmode\hypertarget{ref-NationalEcologicalObservatoryNetworkNEON2021EleLid}{}%
(NEON), N.E.O.N. (2021). Elevation - LiDAR (DP3.30024.001):
RELEASE-2021.

\leavevmode\hypertarget{ref-Olesen2011MisFor}{}%
Olesen, J.M., Bascompte, J., Dupont, Y.L., Elberling, H., Rasmussen, C.
\& Jordano, P. (2011). Missing and forbidden links in mutualistic
networks. \emph{Proceedings of the Royal Society B: Biological
Sciences}, 278, 725--732.

\end{CSLReferences}
